### 2022-08-15 manuscript.Rmd
Move code for Figure 2 to helper script

```{r, eval=FALSE}
# Read grand-averaged power
tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv")) %>%
  mutate(
    phase = factor(phase, levels = c("Pre-insight", "Insight", "Post-insight")),
    condition = factor(condition, levels = c("Informed", "Naive"))
  ) %>%
  filter(!is.na(condition))

channels <- tfr_grand_ave %>%
  select(-average_by, -phase, -condition, -time, -freq) %>%
  colnames()

tfr_grand_ave_informed <- filter(tfr_grand_ave, condition == "Informed")
tfr_grand_ave_naive <- filter(tfr_grand_ave, condition == "Naive")
tfr_grand_ave_diff <- mutate(tfr_grand_ave_informed, condition = "Difference")
tfr_grand_ave_diff[channels] <- tfr_grand_ave_informed[channels] -
  tfr_grand_ave_naive[channels]

bind_rows(tfr_grand_ave, tfr_grand_ave_diff) %>%
  mutate(
    condition = factor(condition, levels = c("Informed", "Naive", "Difference"))
  ) %>%
  pivot_longer(
    cols = all_of(channels), names_to = "electrode", values_to = "amplitude"
  ) %>%
  select(-average_by, -electrode) %>%
  group_by(phase, condition, time, freq) %>%
  summarise(amplitude = mean(amplitude), .groups = "drop") %>%
  ggplot(aes(x = time, y = freq, fill = amplitude)) +
  facet_grid(phase ~ condition) +
  geom_raster() +
  scale_fill_viridis_c(option = "turbo", limits = c(-0.6, 0.6)) +
  coord_cartesian(expand = FALSE)

tmins <- seq(0.0, 1.2, 0.2)
fmins <- seq(4, 36, 4)

channel_locations <- read_csv(here(output_dir, "channel_locations.csv"))

map(c("Pre-insight", "Insight", "Post-insight"), function(this_phase) {
  map(tmins, function(tmin, tstep = 0.2) {
    tmax <- tmin + tstep
    map(fmins, function(fmin, fstep = 4) {
      fmax <- fmin + fstep
      tfr_grand_ave_diff %>%
        filter(time >= tmin & time < tmax & freq >= fmin & freq < fmax) %>%
        filter(phase == this_phase) %>%
        pivot_longer(
          cols = all_of(channels), names_to = "electrode", values_to = "power"
        ) %>%
        left_join(channel_locations, by = c("electrode" = "channel")) %>%
        group_by(electrode, x, y) %>%
        summarise(power = mean(power), .groups = "drop") %>%
        eegUtils::topoplot(
          quantity = "power",
          contour = FALSE,
          interp_limit = "skirt",
          scaling = 0.7
        ) +
        scale_fill_viridis_c(limits = c(-0.3, 0.3), option = "turbo") +
        theme(legend.position = "none")
    }) %>%
      plot_grid(plotlist = ., nrow = 1)
  }) %>%
    plot_grid(plotlist = ., nrow = length(tmins))
})
```

>>>>

```{r, fig2a, fig.height=10, include=TRUE}
# Read grand-averaged power
tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv"))

# Create topographic plots for event-related power in each phase
tfr_plots <- plot_fig2(tfr_grand_ave, tfr_clusters, channel_locations)

# Plot Pre-Insight Phase
tfr_plots[[1]]
```

```{r, fig2b, fig.height=10, include=TRUE}
# Plot Insight Phase
tfr_plots[[2]]
```

```{r, fig2c, fig.height=10, include=TRUE}
# Plot Post-Insight Phase
tfr_plots[[3]]
```
